Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-14 nlp.tex
More PCFG writing.

\subsection{Context-Free Grammar}
ICU date-time formats are well defined both structurally and semantically, and can be defined by a context-free grammar (CFG). A CFG is commonly defined as a set of productions or rules of the form A ? ? where A is a variable, ? is a sequence of variables and terminal symbols (the tokens that make up the alphabet of the language) plus null (? ), and the production symbol (?) indicates that the variable A can be expanded into ? . A CFG can be formally specified with four components: V, T, P, and S, where V is the set of variables, T the set of terminal symbols, P the set of productions, and S the set of available start symbols (a non-empty subset of V) [cite].

@@

%Statistical parsing uses a probabilistic model of syntax in order to assign probabilities to each parse tree.
%Provides principled approach to resolving syntactic ambiguity.
%Allows supervised learning of parsers from tree-banks of parse trees provided by human linguists.
%Also allows unsupervised learning of parsers from corpora.

@@

(add notation for how rules are defined)

Given a CFG grammar $G$, we define  $\tau_G(s)$ as the set of all possible parse trees for input date-time string $s$.  For any $t \in \tau(G)$, the probability $p(t) \ge 1$. In addition, $\sum_{t \in \tau_{G}} = 1$. The parser then chooses the parse tree with the maximum probability, \textit{i.e.} given a date-time string $s$, as input, we determine the highest scoring parse tree $t$ as  $max_{t \in \tau(s)} p(t)$.

@@

\subsection{Training the PCFG}

(used a subset of the public data)

Having defined initial probabilistic weights to the CFG, we train the PCFG with a known training set of date time formats to enhance the coverage of the weights to the various production rules of the grammar.

\subsection{Parsing the PCFG}

\subsection{Extensions to PCFG}

>>>>

\subsection{Context-Free Grammar}
ICU date-time formats are well defined both structurally and semantically, and can be defined by a context-free grammar (CFG). A CFG consists of a set of non-terminal symbols $X$, a set of terminal symbols $\beta$, a start non-terminal symbol $S \in X$ from which the grammar generates the strings, and a set of production rules $\tau$, with each rule of the form $X \rightarrow \beta$ [cite].

@@

@@

The production rules are of the form $ X \rightarrow \beta$ where $X$ is the left-hand side of the rule, while $\beta$ is the right-hand side.

Given a CFG grammar $G$, we define  $\tau_G(s)$ as the set of all possible parse trees for input date-time string $s$.  For any $X \rightarrow \beta \in \tau(G)$, the probability $p(X \rightarrow \beta) \ge 1$. In addition, $\sum_{(X \rightarrow \beta) \in \tau_{G}} = 1$. The parser then chooses the parse tree with the maximum probability, \textit{i.e.} given a date-time string $s$, as input, we determine the highest scoring parse tree $X \rightarrow \beta$ as  $max_{(X \rightarrow \beta) \in \tau(s)} p(X \rightarrow \beta)$.

@@

\subsection{Supervised Learning}

Having defined initial probabilistic weights to the \texttt{PCFG}, we employ supervised learning with a known training set of date time formats to estimate the rule probabilities.  The training corpus is a set of files obtained from an online data analysis corpus, described in Section 5.

The occurrence frequencies of the rules in the correct
(disambiguated) parse trees can be determined from the corpus using the maximum-likelihood parameter estimates.
\begin{equation}
p(X \rightarrow \beta) = \frac{Count(X \rightarrow \beta)}{Count(X)}
\end{equation}

where $Count(X \rightarrow \beta)$ is the number of times that the rule $X \rightarrow \beta$ is seen in
the parse trees $\tau$, and $Count(X)$ is the number of times the non-terminal $X$ is seen in $\tau$. These frequencies can then be normalized into rule probabilities. This method produces accurate probability estimates when trained on a sufficiently large corpus of disambiguated parse trees.

\subsection{Extensions}
